I don't know if projection is categorical. \\ Did \citealt{mandelkern-etal2020} discover that it is?

### 2023-12-22 output/naturalness-paper/paper.tex
re-added output after creating anonymous repo

This paper presents the results of an experiment designed to investigate \citepos{mandelkern-etal2020} claim that the measure they proposed provides evidence that projection is categorical and distinguishes presuppositions from nonpresuppositions.\footnote{\label{f:github}The experiment was approved by the ethics review committee of [university name suppressed]. The experiment, materials, data, and analysis scripts can be accessed here:  \url{xxx} {\bf DO THIS AFTER FINALIZING SCRIPTS}}  To allow for comparison with the results of \citealt{degen-tonhauser-language}, the CCs of the same 20 (non)factive clause-embedding predicates (see Fig.~\ref{fig:dt1a}) were investigated. The experiment also included control stimuli with {\em stop, continue, again, too, also}, and an {\em it-}cleft to allow for comparison with the results of \citealt{mandelkern-etal2020} and the assumptions made in \citealt{simons01} and \citealt{abusch10}.

@@

As shown in Table \ref{t:pairwise},\footnote{While the naturalness ratings collected from the participants range from 0 to 1, the greater than $|$1$|$  estimated marginal mean differences are the result of the beta regression using a logit link function for the mean parameter. The full model output is available here: \url{LINK TO TABLE IN REPO} {\bf ADD THIS AFTER FINALIZING SCRIPTS}.} the pairwise comparison suggests differences between the naturalness ratings of the CCs of the five factive predicates: The ratings of {\em be annoyed} are lower than those of {\em know}, which in turn are lower than those of {\em see} and {\em discover}, which in turn are lower than those of {\em reveal}. There is also variation between the factive predicates and the presuppositional controls: While all five factive predicates are more natural in explicit ignorance contexts than {\em continue, too} and {\em also}, {\em know} is additionally more natural than {\em again} and {\em stop}, and {\em see, discover} and {\em reveal} are additionally more natural than the {\em it-}cleft. Finally, the naturalness ratings in explicit ignorance contexts for {\em see} and {\em discover} do not differ from those of the nonfactives {\em confess, inform}, and {\em acknowledge}, and those of {\em reveal} do not differ from those of the nonfactives {\em admit, hear}, and {\em prove}. These results suggest that naturalness ratings in explicit ignorance contexts do not provide empirical support for categorical projection or for a categorical distinction between factive and nonfactive predicates.

@@

These observations were confirmed by 20 posthoc pairwise comparisons of the estimated means for each context, again using the `emmeans' package (\citealt{emmeans}); a separate pairwise comparison was conducted for each of the 20 expressions. The input to the pairwise comparisons were 20 Bayesian mixed-effects beta regression models with weakly informative priors that were fit using the `brms' package (\citealt{buerkner2017}). The models predicted, for each predicate, the naturalness ratings\footnote{As in the model reported in the previous section, the ratings were transformed to the interval (0,1); see footnote \ref{fn:transform}.} from a fixed effect of context (with treatment coding and `explicit ignorance' as reference level) and included a random by-item intercept (where an item is a complement clause) and a random slope for context by item. The output of the pairwise comparison for each expression were 95\% HDIs of estimated marginal mean differences between each of the three contexts. We assume that two contexts differ if their HDI does not include 0.\footnote{The full model output is available here: \url{LINK TO TABLE IN REPO}.{\bf ADD AFTER FINALIZING SCRIPTS}} As shown in Fig.~\ref{fig:acc-by-context}, naturalness ratings in explicit ignorance vs.\ lower or higher prior probability contexts do not provide support for a categorical distinction between presuppositions and nonpresuppositions.

>>>>

This paper presents the results of an experiment designed to investigate \citepos{mandelkern-etal2020} claim that the measure they proposed provides evidence that projection is categorical and distinguishes presuppositions from nonpresuppositions.\footnote{\label{f:github}The experiment was approved by the ethics review committee of [university name suppressed]. The experiment, materials, data, and analysis scripts can be accessed here:  \url{https://anonymous.4open.science/r/naturalness-in-EIC-5847}.}  To allow for comparison with the results of \citealt{degen-tonhauser-language}, the CCs of the same 20 (non)factive clause-embedding predicates (see Fig.~\ref{fig:dt1a}) were investigated. The experiment also included control stimuli with {\em stop, continue, again, too, also}, and an {\em it-}cleft to allow for comparison with the results of \citealt{mandelkern-etal2020} and the assumptions made in \citealt{simons01} and \citealt{abusch10}.

@@

As shown in Table \ref{t:pairwise},\footnote{While the naturalness ratings collected from the participants range from 0 to 1, the greater than $|$1$|$  estimated marginal mean differences are the result of the beta regression using a logit link function for the mean parameter. The full model output is available here: \url{https://anonymous.4open.science/r/naturalness-in-EIC-5847/results/main/models/analysis1/fullModelOutput/fullModelOutput.pdf}.} the pairwise comparison suggests differences between the naturalness ratings of the CCs of the five factive predicates: The ratings of {\em be annoyed} are lower than those of {\em know}, which in turn are lower than those of {\em see} and {\em discover}, which in turn are lower than those of {\em reveal}. There is also variation between the factive predicates and the presuppositional controls: While all five factive predicates are more natural in explicit ignorance contexts than {\em continue, too} and {\em also}, {\em know} is additionally more natural than {\em again} and {\em stop}, and {\em see, discover} and {\em reveal} are additionally more natural than the {\em it-}cleft. Finally, the naturalness ratings in explicit ignorance contexts for {\em see} and {\em discover} do not differ from those of the nonfactives {\em confess, inform}, and {\em acknowledge}, and those of {\em reveal} do not differ from those of the nonfactives {\em admit, hear}, and {\em prove}. These results suggest that naturalness ratings in explicit ignorance contexts do not provide empirical support for categorical projection or for a categorical distinction between factive and nonfactive predicates.

@@

These observations were confirmed by posthoc pairwise comparisons of the estimated means for each context using the `emmeans' package (\citealt{emmeans}); a separate comparison was conducted for each of the 20 predicates. The input to the pairwise comparisons were 20 Bayesian mixed-effects beta regression models with weakly informative priors that were fit using the `brms' package (\citealt{buerkner2017}). The models predicted  naturalness ratings\footnote{As in the model reported in the previous section, the ratings were transformed to the interval (0,1); see footnote \ref{fn:transform}.} from a fixed effect of context (with treatment coding and `explicit ignorance' as reference level) and included a random by-item intercept (where an item is a complement clause) and a random by-item slope for context.\footnote{By-participant random effects were not included because each participant saw each predicate only once and in only one context condition.} The output of the pairwise comparison for each expression was the 95\% HDI of estimated marginal mean differences between each of the three contexts. We assume that two contexts differ if their HDI does not include 0.\footnote{The full model output is available here: \url{https://anonymous.4open.science/r/naturalness-in-EIC-5847/results/main/models/analysis2/fullModelOutput/fullModelOutput.pdf}.}
